PANCHANGE_analysis

### 2020-11-05 PANCHANGE_analysis.Rmd
added age^2 to model
only did for GAD baseline incase this was not how it should be approached.

Sensitivity analysis for individuals who signed up to GLAD (prepan) either 3, 6 or 9 months before the pendemic began. 
```{r subsample for pre-pan sensitivity analysis}
# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_3months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_3_months_numeric == 1 # Only participants who signed up between December 1st 2019 and March 1st 2020
  )

# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_6months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_6_months_numeric == 1 # Only participants who signed up between September 1st 2019 and March 1st 2020
  )

# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_9months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_9_months_numeric == 1 # Only participants who signed up between June 1st 2019 and March 1st 2020
  )

```

@@

Model naming conventions:
0 - unadjusted
1 - adjusted
a - hierarchical disorders
b - overlapping disorder categories

@@

```{r model1a function}
model1a.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("Disorder_hierarchical",
                            "Gender_collapsed",
                            "age_category_collapsed_reordered",
                            "Ethnicity_collapsed",
                            "time_diff_coping_lockdown_march_23"
                            )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

  assign(paste0(outcome,"model1a_estimates"),
         tidy(get(paste0(outcome,".model1a")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
               "Disorder_hierarchicalEating disorders" = "Eating disorders",
               "Disorder_hierarchicalOCDs" = "OCDs",
               "Disorder_hierarchicalPTSD" = "PTSD",
               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
               "Gender_collapsedFemale" = "Female",
               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
               "age_category_collapsed_reordered19-25" = "19-25 years",
               "age_category_collapsed_reordered26-35" = "26-35 years",
               "age_category_collapsed_reordered36-45" = "36-45 years",
               "age_category_collapsed_reordered46-55" = "46-55 years",
               "age_category_collapsed_reordered56-65" = "56-65 years",
               "age_category_collapsed_reordered66-70" = "66-70 years",
               "age_category_collapsed_reordered71-75" = "71-75 years",
               "age_category_collapsed_reordered76+" = "76+ years",
               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
               "Ethnicity_collapsedAfrican or African British" = "African or African British",
               "Ethnicity_collapsedOther" = "Other ethnicity",
               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

@@

```{r model1b function}
model1b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed_reordered",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

               "age_category_collapsed_reordered19-25" = "19-25 years",
               "age_category_collapsed_reordered26-35" = "26-35 years",
               "age_category_collapsed_reordered36-45" = "36-45 years",
               "age_category_collapsed_reordered46-55" = "46-55 years",
               "age_category_collapsed_reordered56-65" = "56-65 years",
               "age_category_collapsed_reordered66-70" = "66-70 years",
               "age_category_collapsed_reordered71-75" = "71-75 years",
               "age_category_collapsed_reordered76+" = "76+ years",

@@

@@

```{r model1a.explan function}
model1a.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "Disorder_hierarchical",
                             "Gender_collapsed",
                             "age_category_collapsed_reordered",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

  assign(paste0(outcome,".",explan_var,"model1a.explan_estimates"),
         tidy(get(paste0(outcome,".",explan_var,".model1a.explan")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
               "Disorder_hierarchicalEating disorders" = "Eating disorders",
               "Disorder_hierarchicalOCDs" = "OCDs",
               "Disorder_hierarchicalPTSD" = "PTSD",
               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
               "Gender_collapsedFemale" = "Female",
               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
               "age_category_collapsed_reordered19-25" = "19-25 years",
               "age_category_collapsed_reordered26-35" = "26-35 years",
               "age_category_collapsed_reordered36-45" = "36-45 years",
               "age_category_collapsed_reordered46-55" = "46-55 years",
               "age_category_collapsed_reordered56-65" = "56-65 years",
               "age_category_collapsed_reordered66-70" = "66-70 years",
               "age_category_collapsed_reordered71-75" = "71-75 years",
               "age_category_collapsed_reordered76+" = "76+ years",
               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
               "Ethnicity_collapsedAfrican or African British" = "African or African British",
               "Ethnicity_collapsedOther" = "Other ethnicity",
               "key_workerKey worker" = "Key worker",
               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

@@

```{r model1b.explan function}
model1b.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed_reordered",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r gad model1a absolute whole sample}
# Regression coefficients
gad_baseline_model1a_estimates <- model1a.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model1a_estimates)
gad_baseline_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r gad model1b absolute whole sample}
# Regression coefficients
gad_baseline_model1b_estimates <- model1b.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model1b_estimates)
gad_baseline_model1b_estimates

@@

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r gad model1a diff_score prepan}
# Regression coefficients
gad_prepan_model1a_estimates <- model1a.estimates(outcome = "gad.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(gad_prepan_model1a_estimates)
gad_prepan_model1a_estimates

>>>>

dim(dat.retro_sensitivity)
```
age^2 sensitivity 
Exclude individuals with NA for continuous Age variable
```{r}
dat_age_sensitivity <- dat %>%
  filter(!is.na(Age))
dim(dat_age_sensitivity)
```

@@

Model naming conventions:
0 - unadjusted
1 - adjusted
2 - adjusted with age^2
a - hierarchical disorders
b - overlapping disorder categories

@@

```{r model1a function}
model1a.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("Disorder_hierarchical",
                            "Gender_collapsed",
                            "age_category_collapsed",
                            "Ethnicity_collapsed",
                            "time_diff_coping_lockdown_march_23"
                            )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

  assign(paste0(outcome,"model1a_estimates"),
         tidy(get(paste0(outcome,".model1a")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
               "Disorder_hierarchicalEating disorders" = "Eating disorders",
               "Disorder_hierarchicalOCDs" = "OCDs",
               "Disorder_hierarchicalPTSD" = "PTSD",
               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
               "Gender_collapsedFemale" = "Female",
               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
               "Ethnicity_collapsedAfrican or African British" = "African or African British",
               "Ethnicity_collapsedOther" = "Other ethnicity",
               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

@@

```{r model1b function}
model1b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",

@@

```{r model2a function}
model2a.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("Disorder_hierarchical",
                            "Gender_collapsed",
                            "poly(Age, 2)",
                            "Ethnicity_collapsed",
                            "time_diff_coping_lockdown_march_23"
                            )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

  # run the glm
  assign(paste0(outcome,".model2a"),
         lm( formula = glm.formula,
             data = get(data_set)
         )
  )

  assign(paste0(outcome,"model2a_estimates"),
         tidy(get(paste0(outcome,".model2a")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
               "Disorder_hierarchicalEating disorders" = "Eating disorders",
               "Disorder_hierarchicalOCDs" = "OCDs",
               "Disorder_hierarchicalPTSD" = "PTSD",
               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
               "Gender_collapsedFemale" = "Female",
               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
               "poly(Age, 2)1" = "Age",
               "poly(Age, 2)2" = "Age^2", 
               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
               "Ethnicity_collapsedAfrican or African British" = "African or African British",
               "Ethnicity_collapsedOther" = "Other ethnicity",
               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

  return(get(paste0(outcome,"model2a_estimates")))
}

model2a.reg.stats <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("Disorder_hierarchical")
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

  # run the glm
  assign(paste0(outcome,".model2a"),
         lm( formula = glm.formula,
             data = get(data_set)
         )
  )

  assign(paste0(outcome,"model2a_reg_stats"),
         glance(get(paste0(outcome,".model2a"))) %>%
           mutate(
             "n" = format(
               round(nobs,
                     digits = 0),
               nsmall = 0),
             "R2" = format(
               round(r.squared,
                     digits = 2),
               nsmall = 2),
             "adjust. R2" = format(
               round(adj.r.squared,
                     digits = 2),
               nsmall = 2),
             "F" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "n",
             "R2",
             "adjust. R2",
             "F",
             "p value",
             "df"
           )
  )

  return(get(paste0(outcome,"model2a_reg_stats")))
}
```

```{r model2b function}
model2b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "poly(Age, 2)",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

  # run the glm
  assign(paste0(outcome,".model2b"),
         lm( formula = glm.formula,
             data = get(data_set)
         )
  )

  assign(paste0(outcome,"model2b_estimates"),
         tidy(get(paste0(outcome,".model2b")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
               "depressive_disordersDepressive disorder" = "Depressive disorders",
               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
               "eating_disordersEating disorder" = "Eating disorders",
               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
               "Gender_collapsedFemale" = "Female",
               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
               "poly(Age, 2)1" = "Age",
               "poly(Age, 2)2" = "Age^2", 
               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
               "Ethnicity_collapsedAfrican or African British" = "African or African British",
               "Ethnicity_collapsedOther" = "Other ethnicity",
               "key_workerKey worker" = "Key worker",
               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

  return(get(paste0(outcome,"model2b_estimates")))
}

model2b.reg.stats <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("Disorder_hierarchical")
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

  # run the glm
  assign(paste0(outcome,".model2b"),
         lm( formula = glm.formula,
             data = get(data_set)
         )
  )

  assign(paste0(outcome,"model2b_reg_stats"),
         glance(get(paste0(outcome,".model2b"))) %>%
           mutate(
             "n" = format(
               round(nobs,
                     digits = 0),
               nsmall = 0),
             "R2" = format(
               round(r.squared,
                     digits = 2),
               nsmall = 2),
             "adjust. R2" = format(
               round(adj.r.squared,
                     digits = 2),
               nsmall = 2),
             "F" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "n",
             "R2",
             "adjust. R2",
             "F",
             "p value",
             "df"
           )
  )

  return(get(paste0(outcome,"model2b_reg_stats")))
}
```

@@

```{r model1a.explan function}
model1a.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "Disorder_hierarchical",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

  assign(paste0(outcome,".",explan_var,"model1a.explan_estimates"),
         tidy(get(paste0(outcome,".",explan_var,".model1a.explan")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
               "Disorder_hierarchicalEating disorders" = "Eating disorders",
               "Disorder_hierarchicalOCDs" = "OCDs",
               "Disorder_hierarchicalPTSD" = "PTSD",
               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
               "Gender_collapsedFemale" = "Female",
               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
               "Ethnicity_collapsedAfrican or African British" = "African or African British",
               "Ethnicity_collapsedOther" = "Other ethnicity",
               "key_workerKey worker" = "Key worker",
               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

@@

```{r model1b.explan function}
model1b.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1a absolute whole sample}
# Regression coefficients
gad_baseline_model1a_estimates <- model1a.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model1a_estimates)
gad_baseline_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1b absolute whole sample}
# Regression coefficients
gad_baseline_model1b_estimates <- model1b.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model1b_estimates)
gad_baseline_model1b_estimates

@@

### Model 2a: Disorder hierarchical, Adjusted with Age^2 
```{r}
# Regression coefficients
gad_baseline_model2a_estimates <- model2a.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat_age_sensitivity")
kable(gad_baseline_model2a_estimates)
gad_baseline_model2a_estimates

# Regression diagnostic statistics
gad_baseline_model2a_reg_stats <- model2a.reg.stats(outcome = "gad.sum_score_base",
                                                 data_set = "dat_age_sensitivity")
kable(gad_baseline_model2a_reg_stats)
gad_baseline_model2a_reg_stats
```
### Model 2b: Disorder hierarchical, Adjusted with Age^2 
```{r}
# Regression coefficients
gad_baseline_model2b_estimates <- model2b.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat_age_sensitivity")
kable(gad_baseline_model2b_estimates)
gad_baseline_model2b_estimates

# Regression diagnostic statistics
gad_baseline_model2b_reg_stats <- model2b.reg.stats(outcome = "gad.sum_score_base",
                                                 data_set = "dat_age_sensitivity")
kable(gad_baseline_model2b_reg_stats)
gad_baseline_model2b_reg_stats
```

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1a diff_score prepan}
# Regression coefficients
gad_prepan_model1a_estimates <- model1a.estimates(outcome = "gad.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(gad_prepan_model1a_estimates)
gad_prepan_model1a_estimates
